---
title: "Extracting MS results — primary *P* env tables (range rows + between-*P* divider)"
subtitle: "Companion to `extracting_ms_results.Rmd` in this folder: **Range (max − min)** after each production-target block, then a divider before **Δ (P=1 − P≈0.1)** and **Median timber**."
output:
  html_document:
    toc: true
    toc_float: true
    self_contained: true
---

Saved as **`Scripts/Nature_Revision2/extracting_ms_results/extracting_ms_results_primary_P_range_tables.Rmd`**.  
Knitted output: **`extracting_ms_results_primary_P_range_tables.html`** (same folder).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

suppressPackageStartupMessages({
  library(knitr)
})

helper_candidates <- unique(c(
  tryCatch(file.path(knitr::current_input(dir = TRUE), "nr2_rmd_project_root.R"), error = function(e) NA_character_),
  file.path(getwd(), "nr2_rmd_project_root.R"),
  file.path(getwd(), "extracting_ms_results", "nr2_rmd_project_root.R"),
  file.path(getwd(), "Scripts", "Nature_Revision2", "extracting_ms_results", "nr2_rmd_project_root.R"),
  normalizePath(file.path(getwd(), "..", "..", "Scripts", "Nature_Revision2", "extracting_ms_results", "nr2_rmd_project_root.R"), mustWork = FALSE)
))
helper_candidates <- helper_candidates[!is.na(helper_candidates) & nzchar(helper_candidates)]
helper_hit <- helper_candidates[file.exists(helper_candidates)][1L]
if (is.na(helper_hit)) {
  stop(
    "Could not find nr2_rmd_project_root.R. Tried:\n",
    paste(" -", helper_candidates, collapse = "\n"),
    call. = FALSE
  )
}
source(helper_hit, local = FALSE)

root_dir <- nr2_project_root()
knitr::opts_knit$set(root.dir = root_dir)
```

Tables come from `build_primary_p_change_env_tables()` in `Scripts/Nature_Revision2/primary_change_p_env_extract.R` (working directory = project root).

```{r env-tables, results='asis'}
setwd(root_dir)
source(file.path(root_dir, "Scripts", "Nature_Revision2", "primary_change_p_env_extract.R"))
L <- build_primary_p_change_env_tables()

out <- character()
for (i in seq_along(L$sections)) {
  sec <- L$sections[[i]]
  out <- c(
    out,
    paste0("<h2>", sec$title, "</h2>"),
    paste0("<p><em>", sec$subtitle, "</em></p>"),
    as.character(
      knitr::kable(
        sec$wide,
        format = "html",
        escape = FALSE,
        caption = paste0(
          "Starting landscape ", i, ": within each *P* band, rows end with **Range (max − min)**; ",
          "then **Between production targets**, **Δ (max − min), P=1 − P≈0.1**, and **Median timber**."
        )
      )
    )
  )
}
knitr::asis_output(paste(out, collapse = "\n\n"))
```

### Notes (table conventions)

```{r notes}
cat(L$notes, sep = "\n\n")
```

### AllPrimary wide table (convenience)

```{r allprimary-only}
L$minmax_wide
```

### Scenario indices (all landscapes)

```{r detail}
knitr::kable(L$minmax_detail_all, format = "html", escape = FALSE)
```
